\thispagestyle{fancy}

\vspace{0.5cm}

found. That for keywords indicating more extensive categories, details had to be suppressed as much as possible, hardly requires justification. That, conversely, the clarity of the register text has suffered from frequent interlocking, shall be readily admitted.

It may perhaps raise concerns that a series of \textit{adjectives} have been incorporated into the keywords. This was done, however, for such adjectives that are more than mere epithets, that express a particularly characteristic property of the noun. Since, on the other hand, the noun as a word must not be missing, the register in various respects resembles a mathematical table with double, sometimes even multiple, entries.

Regarding emphasis through print, it is to be noted that the keywords, as well as references to such, are rendered by spaced letters. The \textit{italic} print is related to the marking of subsections within larger word articles, whether these sections relate to characteristic areas of the volume, or also to derivations and compositions of the word. It appeared expedient to name those characteristic areas briefly in part. For example, the articles B 1 c and C 4 a, b were summarized under the generic name "Body Theory", furthermore the graphical methods occupying a large space under "Graphics", among others. A specific note at the head of the first register page provides information about the specific use of semicolons, as well as round and square brackets.

From the original intention of giving each citation with mention of the article and its author, abstention was made with consideration of the scope. Precisely regarding the scope, the editor has received the most diverse wishes, ranging approximately from two to ten sheets. The actual scope of not quite 3$\frac{1}{2}$ sheets results in a percentage of somewhat over 6\% in relation to the 70$\frac{1}{2}$ sheets of text in the volume.

For the assessment of the register, reference should be made to its origin; only after a separate register had been prepared for each article were these, as best as possible, drawn together into a whole.

Originally there was an intention to add corrections and supplements to the volume. Meanwhile, what has previously been
