
\thispagestyle{fancy}

\vspace{0.5cm}

\setstretch{0.5}

\titlecontents{subsection}[0pt]
  {}
  {\numberline{}\makebox[1.5cm][l]{\thesubsection}}
  {}
  {\titlerule*[0.5pc]{.}\contentspage}

\fontsize{6}{0}\selectfont 
\bfseries 

\begin{enumerate}[itemsep=0pt,start=31]
    \item Further Determinant Formations\dotfill 44
    \item Determinants of Higher Rank\dotfill 45
    \item Infinite Determinants\dotfill 45
    \item Matrices\dotfill 45
    \item Monographs\dotfill 46
\end{enumerate}

\vspace{-0.1cm}
{\normalfont(Completed in October 1898.)}

\subsection*{\small 3. Irrational Numbers and Convergence of Infinite Processes. \newline \normalfont{By A. Pringsheim in Munich}}

\begin{enumerate}[itemsep=0pt]
    \item Irrational Numbers. Euclid's Ratios and Incommensurable Quantities\dotfill 49
    \item Michael Stifel's Arithmetica Integra\dotfill 50
    \item The Concept of Irrational Numbers in Analytic Geometry\dotfill 51
    \item Cantor-Dedekind Axiom and Arithmetic Theories of Irrational Numbers\dotfill 53
    \item Theories of Weierstrass and Cantor\dotfill 54
    \item Dedekind's Theory\dotfill 55
    \item Du Bois-Reymond's Struggle Against Arithmetic Theories\dotfill 56
    \item Complete Arithmetization in Kronecker's Sense\dotfill 58
    \item 10. Various Representations of Irrational Numbers and Irrationalities of Certain Forms\dotfill 59. 61
    \setcounter{enumi}{10}
    \item Geometric Origin of the Limit Concept\dotfill 63
    \item Arithmetization of the Limit Concept\dotfill 64
    \item Criterion for Limit Value Existence\dotfill 65
    \item The Infinitely Large and Infinitely Small\dotfill 67
    \item Upper and Lower Limits\dotfill 70
    \item Upper and Lower Bounds\dotfill 72
    \item Calculating with Limit Values. The Number $e = \lim(1 + \frac{1}{\nu})^{\nu}$ \dotfill 73
    \item So-called Indeterminate Expressions\dotfill 74
    \item Graduation of Infinite and Null Values\dotfill 75
    \item Limit Values of Doubly Infinite Number Sequences\dotfill 76
    \item Infinite Series. Convergence and Divergence\dotfill 77
    \item 23. Convergence Criteria of Gauss and Cauchy\dotfill 79. 80
    \setcounter{enumi}{23}
    % \item Convergence Criteria of Gauss and Cauchy (Continued)\dotfill 80
    \item Kummer's General Criteria\dotfill 82
    \item Theories of Dini, du Bois-Reymond and Pringsheim\dotfill 83
    \item 27. Criteria of First and Second Kind\dotfill 84. 86
    \setcounter{enumi}{27}
    % \item Criteria of First and Second Kind (Continued)\dotfill 86
    \item Other Criteria Forms\dotfill 88
    \item Scope of Criteria of First and Second Kind\dotfill 89
    \item Limit Areas of Divergence and Convergence\dotfill 90
    \item Conditional and Unconditional Convergence\dotfill 91
    \item Value Changes of Conditionally Convergent Series\dotfill 93
    \item Criteria for Possibly Only Conditional Convergence\dotfill 94
    \item Addition and Multiplication of Infinite Series\dotfill 96
    \item Double Series\dotfill 97
    \item Multiple Series\dotfill 100
    \item Transformation of Series\dotfill 101
    \item Euler-MacLaurin Summation Formula. Half-Convergent Series\dotfill 102
    \item Divergent Series\dotfill 105
    \item Divergent Power Series\dotfill 108
    \item Infinite Products. Historical\dotfill 111
    \item Convergence and Divergence\dotfill 113
    \item Transformation of Infinite Products into Series\dotfill 114
    \item Factorials\dotfill 117
    \item Continued Fractions. General Formal Properties\dotfill 118
    \item Recursive and Independent Calculation of Approximation Fractions\dotfill 121
    \item Approximation Fraction Properties of Special Continued Fractions\dotfill 123
    \item Convergence and Divergence of Infinite Continued Fractions. General Divergence Criterion\dotfill 126
    \item Continued Fractions with Positive Terms\dotfill 128
    \item Convergent Continued Fractions with Terms of Arbitrary Signs\dotfill 129
\end{enumerate}

