\thispagestyle{fancy}

\vspace{0.5cm}

\setstretch{0.5}

\titlecontents{subsection}[0pt]
  {}
  {\numberline{}\makebox[1.5cm][l]{\thesubsection}}
  {}
  {\titlerule*[0.5pc]{.}\contentspage}

\fontsize{6}{0}\selectfont 
\bfseries 

\begin{enumerate}[itemsep=0pt]
    \setcounter{enumi}{5}
    \item Transitivity, Primitivity\dotfill 212
    \item Symmetric and Alternating Group\dotfill 213
    \item Possible Order Numbers of Groups\dotfill 213
    \item Multiply Transitive Groups\dotfill 214
    \item Linear Homogeneous Group\dotfill 214
    \item Group of the Modular Equation\dotfill 216
    \item Other Subgroups of the Linear Homogeneous Group\dotfill 216
    \item Enumeration of Groups of Lowest Degrees\dotfill 216
    \item Isomorphism\dotfill 217
    \item General Group Concept\dotfill 217
    \item Normal Subgroups\dotfill 218
    \item Composition Series\dotfill 220
    \item Isomorphisms of a Group with Itself\dotfill 220
    \item Generating Operations. Geometric Images of Groups\dotfill 221
    \item Abelian Groups\dotfill 222
    \item Sylow's Theorems\dotfill 223
    \item Simple Groups\dotfill 224
    \item Solvable Groups\dotfill 225
    \item Group Determinant\dotfill 226
\end{enumerate}

\vspace{-0.1cm}
{\normalfont(Completed in November 1898.)}

\vspace{-0.1cm}
\section*{B. Algebra}

\subsection*{\small1a. Rational Functions of One Variable; their Zeros. \normalfont{By E. Netto in Giessen}}

\begin{enumerate}[itemsep=0pt]
    \item Definitions\dotfill 228
    \item Constant Counting. Interpolation Problem. Partial Fractions\dotfill 228
    \item Interpolation and Adjustment Calculation\dotfill 230
    \item Difference Calculus\dotfill 231
    \item Roots and their Multiplicity. Zeros\dotfill 232
    \item Derivative and Continuity\dotfill 233
    \item Fundamental Theorem of Algebra\dotfill 233
    \item Factorization\dotfill 238
    \item Field of Rationality\dotfill 239
    \item Reducibility. Irreducibility\dotfill 239
    \item Divisibility Properties\dotfill 241
    \item Greatest Common Divisor\dotfill 241
    \item Irreducible Functions\dotfill 242
    \item Separation of Multiple Roots\dotfill 243
    \item Algebraic Congruences\dotfill 244
    \item Resultant Representation\dotfill 245
    \item Conditions for Common Divisors\dotfill 247
    \item Properties of Resultants\dotfill 248
    \item Calculation of Resultants\dotfill 249
    \item Discriminant\dotfill 251
    \item Properties of the Discriminant\dotfill 251
    \item Discriminant Surface\dotfill 252
    \item Functions with Real Zeros. Reality Relations\dotfill 253
    \item References to Adjacent Areas\dotfill 253
\end{enumerate}

\vspace{-0.1cm}
{\normalfont(Completed in May 1899.)}

\subsection*{\small1b. Rational Functions of Several Variables. \normalfont{By E. Netto in Giessen}}

\begin{enumerate}[itemsep=0pt]
    \item Definitions\dotfill 256
    \item Roots. — Identical Vanishing\dotfill 256
    \item Power Series Development of Certain Rational Functions\dotfill 257
    \item Multiple Roots. — Infinitely Large Roots\dotfill 257
    \item Reducibility and Irreducibility\dotfill 258
    \item Elimination. — Bézout's Method\dotfill 260
\end{enumerate}
