\thispagestyle{fancy}

\vspace{0.5cm}

\setstretch{0.5}

\titlecontents{subsection}[0pt]
  {}
  {\numberline{}\makebox[1.5cm][l]{\thesubsection}}
  {}
  {\titlerule*[0.5pc]{.}\contentspage}

\fontsize{6}{0}\selectfont 
\bfseries 

\begin{enumerate}[itemsep=0pt]
    \setcounter{enumi}{4}
    \item Automorphic Forms. Invariants of Finite Groups\dotfill 336
    \item Form Relationship. Finiteness\dotfill 341
    \item Associated Forms and Typical Representation\dotfill 347
    \item Syzygies\dotfill 350
    \item Enumerative Direction\dotfill 353
    \item Canonization\dotfill 356
    \item Inverse Problems. Irrational Forms\dotfill 358
    \item Invariant Processes. Symbolism and Graphical Representation\dotfill 360
    \item Aronhold's Process. Polars\dotfill 366
    \item Transvection and $\Omega$-Process. Normalization of a Linear Equation\dotfill 367
    \item Substitution of One-sided Derivatives\dotfill 370
    \item Substitution of Homogeneous Derivatives\dotfill 371
    \item Series Developments\dotfill 373
    \item Differential Equations of Comitants\dotfill 375
    \item Extensions, Higher Transformations\dotfill 378
    \item The Extended Projective Group. Reciprocants and Invariants\dotfill 380
    \item Projective Invariants of Curvature Theory\dotfill 383
    \item Differential Forms and Differential Parameters of Surface Theory\dotfill 384
    \item Special Groups and Forms. Semi-invariants\dotfill 386
    \item Combinants and Apolarity\dotfill 390
    \item Resultants and Discriminants\dotfill 395
    \item Reality Questions\dotfill 399
    \item Further Special Forms and Groups\dotfill 400
\end{enumerate}

\vspace{-0.1cm}
{\normalfont(Completed in September 1899.)}

\subsection*{\small3a. Separation and Approximation of Roots. \normalfont{By C. Runge in Hannover}}

\begin{enumerate}[itemsep=0pt]
    \item Introduction\dotfill 405
    \item Separation of Roots. Bounds for the Roots\dotfill 407
    \item The Difference Equation\dotfill 408
    \item Descartes' Rule of Signs and Budan-Fourier's Theorem\dotfill 409
    \item Sturm's Theorem\dotfill 416
    \item Cauchy's Integral\dotfill 418
    \item Theory of Characteristics\dotfill 422
    \item Quadratic Forms in Connection with Sturm's Theorem\dotfill 427
    \item Numerical Example for Separation\dotfill 431
    \item Approximation of Roots. Newton's Method\dotfill 433
    \item More General Methods\dotfill 433
    \item Horner's Scheme\dotfill 436
    \item Bernoulli's Method\dotfill 439
    \item Graeffe's Method\dotfill 440
    \item Approximation for the Case of Several Variables\dotfill 446
\end{enumerate}

\vspace{-0.1cm}
{\normalfont(Completed in September 1899.)}

\subsection*{\small3b. Rational Functions of Roots; Symmetric and Affect Functions. \newline \normalfont{By K. Th. Vahlen in Königsberg}}

\begin{enumerate}[itemsep=0pt]
    \item Symmetric Functions of a Series of Quantities; Definition, Main Theorem, Notation; Numbers\dotfill 450
    \item Formulas and Methods of Cramer, Newton, Girard, Waring, Faà di Bruno\dotfill 450
    \item Reduction of a Function according to Waring and Gauss, according to Cauchy and Kronecker\dotfill 452
    \item Cauchy's Method and its Generalization by Transon\dotfill 452
    \item Generating Functions of Borchardt and Kronecker\dotfill 453
    \item Fundamental Systems\dotfill 455
    \item Theorems on Degree and Weight; Classifications\dotfill 455
    \item Partial Differential Equations and Differential Operators\dotfill 456
    \item Tables; Tabular Laws. The Cayley-Betti Symmetry Law and its Generalization by Mac Mahon\dotfill 460
\end{enumerate}
